---
title: "subset_analysis"
output: html_document
---

```{r setup, include=FALSE}

if(!require("pacman")) install.packages("pacman"); library(pacman)
p_load("tidyverse", "here", "readr",  "workflowr",
          "readxl", "jtools", "broom", "kableExtra", "knitr",
          "sjlabelled", "dplyr", "janitor", "ggplot2", "lme4", "broom.mixed", "ggthemes", "cowplot")

# devtools::install_github("awhstin/awtools")

source(here('code/functions.R'))

options(scipen = 999)


knitr::opts_chunk$set(echo = TRUE)
```

```{r load and filter data, include=FALSE, echo=FALSE}


scenarios <- import(here('data/scenarios.RData'))


```

```{r theming, cache = FALSE}

theme_update(
  panel.spacing = unit(10, "pt"),
  legend.position = "bottom",
  legend.title = element_blank(),
  legend.justification = 0.5,
  legend.text = element_text(size = 6),
  strip.text = element_text(size = 6, face = "bold"),
  plot.title = element_text(size = 10, face = "bold"),
  plot.title.position = "plot",
  axis.text.y = element_text(size = 7, face = "bold"),
  axis.text.x = element_text(size = 6),
  axis.title.x = element_text(size = 7),
  axis.title.y = element_text(size = 8),
  panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line.y = element_line("grey", size = 0.2),
  axis.line.x = element_line("grey", size = 0.2),
  panel.background = element_rect(fill = 'white', colour = 'white'),
  strip.background = element_rect(fill = 'white', colour = 'white')
)



```



```{r}

scenarios <- scenarios %>% 
    mutate(gender_bi = factor(gender,
       levels = c("Male", "Female", "Other"),
  labels = c("Male", "Female or Other", "Female or Other")
    )) %>% 
  mutate(holocaust_is_fact = fct_relevel(holocaust_is_fact,
        c("True", "Do not know", "False"))) %>% 
    mutate(climate_change_true = fct_relevel(climate_change_true,
        c("True", "Do not know", "False")))
  
# levels(scenarios$holocaust_is_fact)

```

```{r, functions for moderation analysis}


glm_table <- function(glm_0, glm_1) {
  glm0_tbl <- tidy(glm_0, conf.level = 0.95, conf.int = TRUE) %>%
    dplyr::select(-statistic,-p.value) %>%
    mutate(variance = std.error ** 2) %>%
    mutate(var = diag(vcov(glm_0)))
  
  glm1_tbl <- tidy(glm_1, conf.level = 0.95, conf.int = TRUE) %>%
    dplyr::select(-statistic,-p.value) %>%
    mutate(variance = std.error ** 2) %>%
    mutate(var = diag(vcov(glm_1)))
  
  colnames(glm1_tbl) <-
    c("term1",
      "estimate1",
      "std.error1",
      "conf.low1",
      "conf.high1",
      "variance1",
      "var1")
  
  glm_tbl <- cbind(glm0_tbl, glm1_tbl)
}

atme_table <- function(glm_tbl) {
  diff_table <- glm_tbl %>%
    dplyr::select(-term1) %>%
    mutate(ATME = estimate1 - estimate) %>%
    mutate(pooled_std.error = sqrt(var + var1)) %>%
    mutate(ATME_lower = ATME - (1.96 * pooled_std.error)) %>% #calculate 95% confidence intervals
    mutate(ATME_upper = ATME + (1.96 * pooled_std.error))
}


```



the idea is to make one plot for severity of harms 4 scenarios moderation by beliefs and partisanship

```{r, glm severity of harms, anti-vax}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <-
  scenarios %>% filter(level_4 == "Anti-vaccination") %>%
  filter(level_7 == "None")

subset_1 <-
  scenarios %>% filter(level_4 == "Anti-vaccination") %>%
  filter(level_7 == "Severe")
#+ ideology  + age + education + gender_bi

glm_0 <-
  glm(choice ~ vaccines_cause_infertility + party  + age + education + gender_bi,
      data = subset_0)

glm_1 <-
  glm(choice ~ vaccines_cause_infertility + party  + age + education + gender_bi,
      data = subset_1)



glm_tbl <- glm_table(glm_0, glm_1)


diff_table_S_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility") |
           str_detect(term, "party")) %>%
  mutate(scenario = "Anti-vaccination")


```


```{r, glm severity of harms, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_7 == "None")

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_7 == "Severe")

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_S_election <- atme_table(glm_tbl) %>%   #
    filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm severity of harms, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_7 == "None")

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_7 == "Severe")

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_S_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm severity of harms, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_7 == "None")

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_7 == "Severe")

# levels(subset_1$gender_bi)

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_S_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```


now the same for pattern of behavior 4 scenarios moderation by beliefs and partisanship

```{r, glm pattern, anti-vax}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_6 == "First time")

subset_1 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_6 != "First time")

glm_0 <-
  glm(
    choice ~ vaccines_cause_infertility + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ vaccines_cause_infertility + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_P_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility")|str_detect(term, "party")) %>% 
  mutate(scenario = "Anti-vaccination")

```

```{r, glm pattern, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_6 == "First time")

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_6 != "First time")

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_P_election <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm pattern, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_6 == "First time")

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_6 != "First time")

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_P_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm pattern, climate}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_6 == "First time")

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_6 != "First time")

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_P_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```



now the same for N of followers 4 scenarios moderation by beliefs and partisanship

```{r, glm N of fol, anti-vax}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_3 != "> 1,000,000")

subset_1 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_3 == "> 1,000,000")

glm_0 <-
  glm(
    choice ~ vaccines_cause_infertility + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ vaccines_cause_infertility + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_N_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility")|str_detect(term, "party")) %>% 
  mutate(scenario = "Anti-vaccination")

```

```{r, glm N of fol, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_3 != "> 1,000,000")

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_3 == "> 1,000,000")

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_N_election <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm N of fol, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_3 != "> 1,000,000")

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_3 == "> 1,000,000")

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)


diff_table_N_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm N of fol, climate}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_3 != "> 1,000,000")

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_3 == "> 1,000,000")

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_N_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```


now the same for the account type 4 scenarios moderation by beliefs and partisanship

```{r, glm account, anti-vax}
levels(scenarios$level_1)
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(str_detect(level_1, "Politic", negate = TRUE))

subset_1 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(str_detect(level_1, "Politic"))

glm_0 <-
  glm(
    choice ~ vaccines_cause_infertility + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ vaccines_cause_infertility + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_A_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility")|str_detect(term, "party")) %>% 
  mutate(scenario = "Anti-vaccination")

```

```{r, glm account, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(str_detect(level_1, "Politic", negate = TRUE))

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(str_detect(level_1, "Politic"))

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_A_election <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm  account, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(str_detect(level_1, "Politic", negate = TRUE))

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(str_detect(level_1, "Politic"))

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_A_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm N of fol, climate}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(str_detect(level_1, "Politic", negate = TRUE))

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(str_detect(level_1, "Politic"))

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_A_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```



now the same for account's partisanship 4 scenarios moderation by beliefs and partisanship

```{r, glm acc party, anti-vax}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_2 == "Democrat")

subset_1 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_2 == "Republican")

glm_0 <-
  glm(
    choice ~ vaccines_cause_infertility + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ vaccines_cause_infertility + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_AP_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility")|str_detect(term, "party")) %>% 
  mutate(scenario = "Anti-vaccination")

```

```{r, glm acc party, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_2 == "Democrat")

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_2 == "Republican")

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_AP_election <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm acc party, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_2 == "Democrat")

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_2 == "Republican")

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_AP_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm pattern, climate}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_2 == "Democrat")

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_2 == "Republican")

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_AP_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```




now the same for level of falseness 4 scenarios moderation by beliefs and partisanship

```{r, glm false, anti-vax}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_5 == "Misleading")

subset_1 <- scenarios %>% filter(level_4 == "Anti-vaccination") %>% 
  filter(level_5 != "Misleading")

glm_0 <-
  glm(
    choice ~ vaccines_cause_infertility + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ vaccines_cause_infertility + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_F_antivax <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "vaccines_cause_infertility")|str_detect(term, "party")) %>% 
  mutate(scenario = "Anti-vaccination")

```

```{r, glm false, election}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_5 == "Misleading")

subset_1 <- scenarios %>% filter(level_4 == "Election denial") %>% 
  filter(level_5 != "Misleading")

glm_0 <-
  glm(
    choice ~ election_was_stolen + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ election_was_stolen + party   + age + education + gender_bi, data = subset_1
  )

glm_tbl <- glm_table(glm_0, glm_1)

diff_table_F_election <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "election_was_stolen")|str_detect(term, "party"))%>% 
  mutate(scenario = "Election denial")

```

```{r, glm false, holocaust}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_5 == "Misleading")

subset_1 <- scenarios %>% filter(level_4 == "Holocaust denial") %>% 
  filter(level_5 != "Misleading")

glm_0 <-
  glm(
    choice ~ holocaust_is_fact + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ holocaust_is_fact + party   + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_F_holocaust <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "holocaust_is_fact")|str_detect(term, "party"))%>% 
  mutate(scenario = "Holocaust denial")

```

```{r, glm false, climate}
#subset data by treatment level, here by N of followers, where over 1 mil = 1, else = 0 control codiron 0 = less than 1 mil
subset_0 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_5 == "Misleading")

subset_1 <- scenarios %>% filter(level_4 == "Climate change denial") %>% 
  filter(level_5 != "Misleading")

glm_0 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_0
  )

glm_1 <-
  glm(
    choice ~ climate_change_true + party  + age + education + gender_bi, data = subset_1
  )

  
glm_tbl <- glm_table(glm_0, glm_1)

diff_table_F_climate <- atme_table(glm_tbl) %>%
  filter(str_detect(term, "climate_change_true")|str_detect(term, "party"))%>% 
  mutate(scenario = "Climate change denial") 

```

```{r}

diff_table_A <-rbind(diff_table_A_election, diff_table_A_antivax, diff_table_A_holocaust, diff_table_A_climate) %>% 
  mutate(attribute = "Account\n(Political\nrelative to\nNonpolitical)")

diff_table_N <-rbind(diff_table_N_election, diff_table_N_antivax, diff_table_N_holocaust, diff_table_N_climate) %>% 
  mutate(attribute = "Number\nof followers\n(> 1 million\nrelative to\n< 1 million)")

diff_table_P <-rbind(diff_table_P_election, diff_table_P_antivax, diff_table_P_holocaust, diff_table_P_climate) %>% 
  mutate(attribute = "Pattern\nof behavior\n(Repeated\nrelative to\nFirst time)")

diff_table_S <-rbind(diff_table_S_election, diff_table_S_antivax, diff_table_S_holocaust, diff_table_S_climate) %>% 
  mutate(attribute = "Severity\nof harms\n(Severe\nrelative to\nNone)")

diff_table_AP <-rbind(diff_table_AP_election, diff_table_AP_antivax, diff_table_AP_holocaust, diff_table_AP_climate) %>% 
  mutate(attribute = "Account's\npartisanship\n(Republican\nrelative to\nDemocrat)")

diff_table_F <-rbind(diff_table_F_election, diff_table_F_antivax, diff_table_F_holocaust, diff_table_F_climate) %>% 
  mutate(attribute = "Level\nof falseness\n(Completely false\nrelative to\nMisleading)")

```

```{r}


diff_table_all <-
  rbind(diff_table_A,
        diff_table_AP,
        diff_table_N,
        diff_table_F,
        diff_table_P,
        diff_table_S) %>%
  mutate(scenario = as.factor(scenario)) %>%
  mutate(scenario = fct_relevel(
    scenario,
    c(
      "Election denial",
      "Anti-vaccination",
      "Holocaust denial",
      "Climate change denial"
    )
  )) %>%
  mutate(ATME_round = round(ATME, 2)) %>%
  mutate(attribute = as.factor(attribute))



diff_table_all_acc <- diff_table_all %>%
  filter(str_detect(term, "True") |
           str_detect(term, "Do not know") | str_detect(term, "False")) %>%
  mutate(
    belief = ifelse(
      str_detect(term, "Do not know"),
      "Do not know (relative to accurate belief)",
      "Inaccurate belief (relative to accurate belief)"
    )
  ) %>%
  mutate(belief = as.factor(belief)) %>%
  mutate(
    party = ifelse(
      str_detect(term, "Independent"),
      "Independent (relative to Democrat)",
      "Republican (relative to Democrat)"
    )
  )



diff_table_all_party <- diff_table_all  %>%
  filter(str_detect(term, "party")) %>%
  mutate(
    party = ifelse(
      str_detect(term, "Independent"),
      "Independent (relative to Democrat)",
      "Republican (relative to Democrat)"
    )
  )
```

```{r, plot atmes choice}



data <-
  filter(diff_table_all_acc, belief == str_detect(belief, "Inaccurate"))

atme_plot_all_acc <- diff_table_all_acc %>%
  ggplot(aes(
    x = reorder(scenario, desc(scenario)),
    y = ATME,
    ymin = ATME_lower,
    ymax = ATME_upper,
    color = belief
  )) +
  facet_grid(~ attribute, scales = "free") +
  scale_y_continuous(breaks = seq(from = -0.1, to = 0.1, by = 0.1),
                     limits = c(-0.18, 0.18)) +
  geom_hline(
    yintercept = 0,
    alpha = .5,
    linetype = "dashed",
    size = 0.2
  ) +
  geom_point(position = position_dodge(width = 0.5), size = 1.3) +
  geom_errorbar(position = position_dodge(width = 0.5),
                size = 0.25,
                width = 0) +
  # geom_pointrange(position = position_dodge(width = 0.5), size = 0.2) +
  geom_text(
    aes(label = ifelse(
      str_detect(belief, "Inaccurate"),
      sprintf("%0.2f", ATME_round),
      ""
    )),
    color = "black",
    size = 1.5,
    nudge_x = 0.23
  ) +
  geom_text(
    aes(label = ifelse(
      str_detect(belief, "Do not know"),
      sprintf("%0.2f", ATME_round),
      ""
    )),
    color = "black",
    size = 1.5,
    nudge_x = 0.005
  ) +
  coord_flip() +
  scale_color_manual(values = c("darkgrey", "#6c3903")) +
  labs(title = "A. Moderation effects of beliefs on choice to remove posts",
       y = "Moderation by accuracy of the effect of conjoint attributes on probability to remove posts",
       x = "")
atme_plot_all_acc


palette_partisan  <- c("#967cae", "#d04b4b")
atme_plot_all_party <- diff_table_all_party %>%
  ggplot(aes(
    x = reorder(scenario, desc(scenario)),
    y = ATME,
    ymin = ATME_lower,
    ymax = ATME_upper,
    color = party
  )) +
  facet_grid(~ attribute, scales = "free") +
  scale_y_continuous(breaks = seq(from = -0.1, to = 0.1, by = 0.1),
                     limits = c(-0.18, 0.18)) +
  geom_hline(
    yintercept = 0,
    alpha = .5,
    linetype = "dashed",
    size = 0.2
  ) +
  geom_point(position = position_dodge(width = 0.5), size = 1.3) +
  geom_errorbar(position = position_dodge(width = 0.5),
                size = 0.25,
                width = 0) +
  # geom_pointrange(position = position_dodge(width = 0.5), size = 0.2) +
  geom_text(
    aes(label = ifelse(
      str_detect(party, "Republican"),
      sprintf("%0.2f", ATME_round),
      ""
    )),
    color = "black",
    size = 1.5,
    nudge_x = 0.23
  ) +
  geom_text(
    aes(label = ifelse(
      str_detect(party, "Independent"),
      sprintf("%0.2f", ATME_round),
      ""
    )),
    color = "black",
    size = 1.5,
    nudge_x = 0.005
  ) +
  coord_flip() +
  scale_color_manual(values = palette_partisan) +
  labs(title = "B. Moderation effects of partisanship on choice to remove posts",
       y = "Moderation by partisanship of the conjoint attributes on probability to remove posts",
       x = "")
atme_plot_all_party


moderation_choice <-
  plot_grid(
    atme_plot_all_acc,
    atme_plot_all_party,
    ncol = 1,
    scale = c(.98, .98)
  )
moderation_choice

ggsave(
  filename = here("figs/SI_moderation_choice.png"),
  plot = moderation_choice,
  dpi = 300,
  units = 'cm',
  height = 22,
  width = 17.8
)

ggsave(
  filename = here("figs/SI_moderation_choice.pdf"),
  plot = moderation_choice,
  dpi = 300,
  units = 'cm',
  height = 22,
  width = 17.8
)
            
```












